---
title: "Awesome Title"
subtitle: "Where is this talk?"
author: "Nicholas Tierney"
institute: Telethon Kids Institute
format: 
  revealjs:
    theme: [blood, extra.scss]
editor: visual
execute: 
  echo: false
  warning: true
---

```{r}
#| label: library
#| include: false
library(tidyverse)
library(visdat)
library(naniar)
library(gganimate)
library(knitr)
library(ggrepel)
```


```{r}
#| label: helpers
#| include: false

icons_fa <- icons::fontawesome
icon_box <- icons_fa$solid$`box-open`
icon_link <- icons_fa$solid$link
icon_twitter <- icons_fa$brands$twitter
icon_github <- icons_fa$brands$github
icon_plane <- icons_fa$solid$`paper-plane`


as_table <- function(...) knitr::kable(..., format='html', digits = 3)

theme_set(
  theme_grey(base_size = 16) +
  theme(
    legend.position = "bottom",
    plot.background = element_rect(fill = "transparent"),
    legend.background = element_rect(fill = "transparent")
  )
)

# **ni**ck's **pa**lette
nipa <- list(red = "#c03018",
             orange = "#f0a800",
             green = "#609048",
             purple = "#484878",
             light_purple = "#A3A3BB",
             light_green = "#AFC7A3",
             light_orange = "#F7D37F",
             light_red = "#DF978B",
             pale_purple = "#ECECF1",
             pale_green = "#D7E3D1",
             pale_orange = "#FBE9BF",
             pale_red = "#EFCBC4")

```

# Intro

# Background

Put More slides here.

::: {.notes}
Speaker notes go here.
:::

# Take homes

# Future Directions

::: {.fragment .fade-up}
- More features
- More features
- More features
:::

# Test

# Thanks

:::: {.columns}

::: {.column width = "40%"}

- So many great people
- So many great people
- So many great people
- So many great people

:::

::: {.column width = "40%"}

- So many great people
- So many great people
- So many great people
- So many great people

:::

::::

# Resources

- So many things
- So many things
- So many things
- So many things

# Colophon

- Slides made using [quarto](https://github.com/quarto-dev/quarto)
- Colours taken + modified from [lorikeet theme from ochRe](https://github.com/ropenscilabs/ochRe)
[njtierney/njt-talks](github.com/njtierney/njt-talks)
<!-- - Header font is **Josefin Sans** -->
<!-- - Body text font is **Montserrat** -->
<!-- - Code font is **Fira Mono** -->
<!-- - template available:  -->

# Learning more

`r icon_box` [package link]()

`r icon_link` [talk link]()

`r icon_twitter` nj_tierney

`r icon_github` njtierney

`r icon_plane` nicholas.tierney@gmail.com

# **End.**
